### 2016-09-30 results.tex

\begin{figure}[t]
\centering
\fpage{.425}
{
\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
\nudge\nudge $a\gets\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}
%{
%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
%$M \gets \pubaux$\\
%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
%\nudge if $\TestOracle(x)=1$ then Return $\bot$
%}
%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
\caption{Correctness attack for garbled Bloom filters with public~$M$. }
\label{fig:adv-gbf}
\end{figure}
Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
structure called a \emph{garbled Bloom filter} (GBF).   Modulo some implementation
details, a GBF is like a classical Bloom filter, but
rather than storing a bit 1 at the indices determined by $H_j(x)$, the
GBF stores xor-shares of~$x$.  Thus, if $x \in S$, then hashing~$x$
and xoring together the strings stored at the indicated positions
recovers~$x$. We give the pseudocode for the GBF $\Rep$ and $\Qry$
algorithms in Figure~\ref{fig:gbf}.

@@

We admit that attack is not particularly sophisticated, yet it might
be significantly more efficient than brute force guessing over the
universe of inputs (imagine that $\elts=\bits^{128}$), even if you know
that the distribution deviates significantly from uniform. Notice,
too, that you \emph{cannot} mount it against a standard Bloom
filter.

@@

\heading{Privacy. }
We observe immediately that when~$\pubaux=\langle M \rangle$ the GBF cannot be SS-private (in the ROM) because $\privaux=\emptystring$.  In fact, it is easy to see that the correctness attack just given works as a privacy attack, too, with small modifications.  In particular, the attacker cannot check that the reconstructed $x \not\in S$, nor query a~$\TestOracle$.  Thus the efficacy of the attack depends on the false positive rate. \todo{Either work out a proof for this case, or punt and make the attack more formal.}

If instantiated with hash functions $H_j(x) = F_K(\langle j,x \rangle)$ and $\privaux = \langle K \rangle$, the SS-privacy of the GBF follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}\label{thm:lin-privacy}
Fix $k,m,n,r,\lambda>0$ and a function family~$F\colon \calK \times \bits^* \to [m]$.  Let $\setprim_{\mathrm{gbf}}= (\Rep, \Qry)$ be the garbled Bloom filter with hash functions $H_j(x)=F_K(\langle j,x \rangle)$ and $\privaux=langle K \rangle$.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements \fixme{ANIMESH: make this correct}
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.

\begin{verbatim}
%------------------------------------%
\end{verbatim}

@@

>>>>

\begin{figure}[t]
\centering
\hfpagess{.45}{.45}
{
\adversaryv{$A^{\TestOracle,H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$; $L \gets \binom{m}{k}$
for $\ell=1$ to $L$\\
$i_1,i_2,\ldots,i_k \gets \mathcal{I}_L$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
\nudge\nudge $a\gets\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}
{
\adversaryv{$A^{H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$
for $x \in X_1,X_2,\ldots,X_q$\\
\nudge for $j=1$ to $k$ \\
\nudge \nudge $i_j \gets H(j,x)$
\nudge $x' \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if $x' = x$ then Return $x$\\
Return~$X_q$
}
%{
%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
%$M \gets \pubaux$\\
%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
%\nudge if $\TestOracle(x)=1$ then Return $\bot$
%}
%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
\caption{Correctness attack for garbled Bloom filters with public~$M$.  The sequence $\mathcal{I}_1,\mathcal{I}_2,\ldots,\mathcal{I}_L$ is some implicit enumeration of~$k$-tuples of indices over $[m]$.   }
\label{fig:adv-gbf}
\end{figure}
Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
structure called a \emph{garbled Bloom filter} (GBF).   Modulo some implementation
details, a GBF is like a classical Bloom filter, but
rather than storing a bit 1 at the indices determined by $H_j(x)$, the
GBF stores xor-shares of~$x$.  Thus, if $x \in S$, then hashing~$x$
and xoring together the strings stored at the indicated positions
recovers~$x$. We give the pseudocode for the GBF $\Rep$ and $\Qry$
algorithms in Figure~\ref{fig:gbf}.

@@

We admit that attack is not particularly sophisticated, yet it might
be significantly more efficient than brute force guessing.  When $k,m,n$ are as in the example just given, and $\elts=\bits^{128}$, 
this attack will be considerably faster even if the attacker knows that the distribution deviates significantly from uniform.   Note that in the ROM, the order in which $k$-tuples are considered is largely irrelevant, especially when $2^\lambda \gg \binom{m}{k}$.
%Notice,too, that you \emph{cannot} mount it against a standard Bloom filter.

@@

\heading{Privacy. }
We observe immediately that when~$\pubaux=\langle M \rangle$ the GBF cannot be SS-private (in the ROM) because $\privaux=\emptystring$.  In fact, it is easy to see that the correctness attack given in Figure~\ref{fig:adv-gbf} works as a one-wayness attack, too, with small modifications: remove the check for $x \not\in S$, and the call to $\TestOracle$.  To maximize the efficiency of the attack

 Thus the efficacy of the attack depends on the false positive rate. \todo{Either work out a proof for this case, or punt and make the attack more formal.}

If instantiated with hash functions $H_j(x) = F_K(\langle j,x \rangle)$ and $\privaux = \langle K \rangle$, the SS-privacy of the GBF follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}\label{thm:gbf-prf-privacy}
Fix $k,m,n,r,\lambda>0$ and a function family~$F\colon \calK \times \bits^* \to [m]$.  Let $\setprim_{\mathrm{gbf\mbox{-}prf}}= (\Rep, \Qry)$ be the garbled Bloom filter with hash functions $H_j(x)=F_K(\langle j,x \rangle)$ and $\privaux=\langle K \rangle$.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{gbf\mbox{-}prf}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ carries out the pseudocode of~$\Rep$ in Figure~\ref{fig:gbf}, making use of $F_K(s_1),\ldots,F_K(s_{kn})$ in the obvious way.  It returns~$M$ as $\pubaux$.
\end{proof}

\ignore{
\begin{verbatim}
%----- LEFT HERE FOR REMINDERS, AND FOR MENTIONING OPEN PROBLEMS IN INTRO-------------------------------%
\end{verbatim}

@@

\end{itemize}
}
